\section{Procedure}
The following steps were undertaken to conduct the experiment:

\begin{enumerate}

    \item \textbf{Frequency Setup}: 
    Begin by setting the desired frequency of the input signal using the function generator. It is advised to follow a logarithmic scale.
    
    \item \textbf{Input Signal Configuration}: 
    Configure the input signal to align with the chosen frequency and amplitude specifications. Opt for a sinusoidal waveform as input signal. 
    Using the BNC T-splitter establish the connection between the configured signal and the circuit's input and oscilloscope.
    
    \item \textbf{Output Signal Measurement}: 
    Employ an oscilloscope to measure the output signal of the circuit. Connect the oscilloscope to the circuit's output to visualize its response to the input signal.
    
    \item \textbf{Voltage Measurement Across Resistor (Differentiator Circuit)}: 
    For the differentiator circuit, measure the voltage across the resistor using the oscilloscope. 
    
    \item \textbf{Voltage Measurement Across Capacitor (Integrator Circuit)}: 
    For the integrator circuit, introduce an additional resistor in parallel with the capacitor to incorporate an offset voltage and measure the voltage across the capacitor using the oscilloscope. 
    
    \item \textbf{Time Difference Measurement}: 
    Further analyze the phase shift between the input and output signals by measuring the time difference between corresponding points on the two signals using the oscilloscope's cursors.
    
    \item \textbf{Gain Calculation}: 
    Calculate the gain of the circuit in decibels (dB) using the formula: $$ \text{Gain}_{\text{dB}} = 20 \log_{10} \left( \frac{V_{\text{out}}}{V_{\text{in}}} \right) $$
    where $V_{\text{out}}$ represents the measured output voltage and $V_{\text{in}}$ is the input voltage.
    
    \item \textbf{Phase Shift Calculation}: 
    From the time difference measured, determine the phase shift between the input and output signals in radians through the formula:
    $$ \text{Phase shift (radians)} = 2\pi \cdot \text{Time difference} \cdot \text{Frequency}$$
    The phase shift is positive when the output signal crosses zero before the input signal; and negative when the output signal crosses zero after the input signal.

\end{enumerate}
